Retrofitting Effect Handlers onto OCaml

### 2020-11-17 retro-concurrency.tex
edits

The rest of the paper is organized as follows. The next section describes the
details of stock OCaml program stack. In \S\ref{sec:refine}, we refine the
design further focussing on retrofitting effect handlers into a mainstream
\emph{systems} language. \S\ref{sec:semantics} presents the compilation scheme
and operational semantics semantics for Multicore OCaml effect handlers.
\S\ref{sec:impl} discusses the compiler and the runtime system support for
implementing effect handlers. \S\ref{sec:eval} presents extensive performance
evaluation of effect handlers against the goals set in \S\ref{sec:req}.
\S\ref{sec:related} and \S\ref{sec:conc} present the related work and the
conclusions.

@@

Continuations $k$ are either empty $[]$ or non-empty sequence of \emph{fibers}.
A fiber $\fiber \coloneqq (\fl,\hc)$ is a list of frames $\fl$ and a handler
closure $\hc \coloneqq (h,\env)$, which is a pair of handler $h$ and its
environment $\env$.

>>>>

The remainder of the paper continues with a description of the stock OCaml program stack (\S\ref{sec:stack}). We then refine the
design further by focussing on retrofitting effect handlers into a mainstream
\emph{systems} language (\S\ref{sec:refine}), followed by the compilation scheme
and operational semantics semantics for Multicore OCaml effect handlers (\S\ref{sec:semantics}).  We then discuss the compiler and runtime system support for
implementing effect handlers (\S\ref{sec:impl}), and present extensive performance
evaluation of effect handlers (\S\ref{sec:eval}) against our design goals (\S\ref{sec:req}).
Finally, we discuss the related work (\S\ref{sec:related}) and conclude (\S\ref{sec:conc}).

@@

Continuations $k$ are either empty $[]$ or a non-empty sequence of \emph{fibers}.
A fiber $\fiber \coloneqq (\fl,\hc)$ is a list of frames $\fl$ and a handler
closure $\hc \coloneqq (h,\env)$, which is a pair of handler $h$ and its
environment $\env$.
